ms_figures

### 2018-01-24 man/ms_figures.Rmd
add figure 5

>>>>

```{r, warning=FALSE}
cro_sites <- read.csv(here("data/cronos_medias", "cronos_sites.csv"), header = TRUE, sep = ',')

cronos_bai <- cro_sites %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.2, colour=NA) +
  geom_line() + 
  geom_point(size=.8) + 
  theme(panel.grid = element_blank(),
        legend.position = c(0.1,.8),
        strip.background = element_blank()) + 
  scale_colour_manual(values = c('#7570b3','#e7298a','#1b9e77')) +
  scale_fill_manual(values = c('#7570b3','#e7298a','#1b9e77')) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10)) 
  # scale_y_continuous(sec.axis = sec_axis(~ ., name = '# trees', breaks = c(0,15,30))) +
  # geom_line(aes(x=year, y=n_trees+40, colour=site))

samp <- cro_sites %>% ggplot(aes(x=year, y=n_trees, colour=site)) + 
  theme_bw() + ylab('# trees') + 
  geom_line() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        plot.margin = margin(t = 5, r = 0, b = -5, l = 0, unit = "pt")) + 
  scale_colour_manual(values = c('#7570b3','#e7298a','#1b9e77')) +
  scale_fill_manual(values = c('#7570b3','#e7298a','#1b9e77')) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10))

  # theme(plot.margin = unit(c(1,5,-30,6),units="points"),
  #       axis.title.y = element_text(vjust =0.25))

plot_bai_s <- samp + cronos_bai + plot_layout(ncol=1, heights = c(0.1, 0.9))

plot_bai_s
```
